基于MS-GARCH模型的上海银行同业拆借利率波动性分析

### 2019-01-19 ms-garch.Rmd
fixup

---
title: "基于MS-GARCH模型的上海银行同业拆借利率波动性分析"
author: "Jin"
date: "2019-01-14"
output:
  bookdown::html_document2:
    number_sections: true
    seq_numbering: true
    fig_caption: true
    highlight: haddock
    theme: null
    md_extensions: +east_asian_line_breaks
    keep_md: true
    toc: false
    pandoc_args: ["--filter", "pandoc-crossref", "-M", "eqnPrefix="]
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--listing", "--filter", "pandoc-crossref"]
  bookdown::word_document2:
    fig_caption: true
    reference_docx: abc.docx
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--filter", "pandoc-crossref"]
css: markdown.css
autoEqnLabels: true
eqnPrefixTemplate: ($$i$$)
linkReferences: true
bibliography: msgarch.bib
csl: chinese-gb7714-2005-numeric.csl
link-citations: true
---

@@

```{r,eval=T,include=FALSE}
shibor.rt1<-basicStats(shibor.rt)
shibor.rt1
shibor.rt2<- as.data.frame(t(shibor.rt1[c(7,14,16,15),]))
colnames(shibor.rt2) <- c("均值","标准差","偏态系数","峰态系数")
```

```{r stat,eval=T,echo=F,message=FALSE,warning=FALSE,comment=""}
kable(shibor.rt2,row.names =F,align = "c", caption="样本描述性分析结果")
```

>>>>

---
title: "基于MS-GARCH模型的上海银行同业拆借利率波动性分析"
author: "Jin"
date: "2019-01-14"
output:
  bookdown::html_document2:
    number_sections: true
    seq_numbering: true
    fig_caption: true
    highlight: haddock
    theme: null
    md_extensions: +east_asian_line_breaks
    keep_md: true
    toc: false
    pandoc_args: ["--filter", "pandoc-crossref", "-M", "eqnPrefix="]
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--listing", "--filter", "pandoc-crossref"]
  bookdown::word_document2:
    fig_caption: true
    reference_docx: word-styles-01.docx
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--filter", "pandoc-crossref"]
css: markdown.css
autoEqnLabels: true
eqnPrefixTemplate: ($$i$$)
linkReferences: true
bibliography: msgarch.bib
csl: chinese-gb7714-2005-numeric.csl
link-citations: true
---

@@

```{r stat, eval=T,echo=F,message=FALSE,warning=FALSE,comment=""}
shibor.rt1<-basicStats(shibor.rt)
shibor.rt2<- as.data.frame(t(shibor.rt1[c(7,14,16,15),]))
colnames(shibor.rt2) <- c("均值","标准差","偏态系数","峰态系数")

kable(shibor.rt2,row.names =F,align = "c", caption="样本描述性分析结果")
```
